### 2014-04-03 paper/designspace.tex
fiddling, integrating tovi comments, update script

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/tubespace.pdf}
\caption{The design space of pipes.  Pipe openings, design, topologies, and media are discussed more fully in the text.}
\label{fig:pipespace}
\end{figure}

@@

Pipes can have four opening styles: open, return, semi-closed, and fully enclosed (see Figure \ref{fig:pipespace}).  As we are interested in interactive devices, we distinguish a ``user side"---part of the surface or interior of an object facing its user; and a ``system side"---where other hardware such as electronics may be connected.  We refer to a pipe which is ``open on the user side'' to have its contents \emph{physically accessible} to a user \emph{at interaction time}.  ``Closed on the user side'' implies physically cut off from the user.  Similarly with the system side.  User or system manipulation of pipe contents are possible even without physical access, e.g., via soundwaves. \tovi{still not convinced we need this distinction}

@@

\subsection{Design of Pipes}
Pipe design may emphasize either exterior connection points or interior paths.  Focused on the exterior features is the touch sensitive toy in Figure \ref{fig:toys}, where pipes must exit the toy at the frontal lobe and parietal lobes to make those \emph{specific locations} touch-sensitive. Alternatively, the neon sign's output in Figure \ref{fig:neon} is based on the \emph{path} of the pipe. \tovi{still think we can remove this dimension}

>>>>

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/tubespace.pdf}
\caption{The design space of pipes.  See text for details.}
\label{fig:pipespace}
\end{figure}

@@

Pipes can have four opening styles: open, return, semi-closed, and fully enclosed (see Figure \ref{fig:pipespace}).  As we are interested in interactive devices, we distinguish a ``user side"---part of the surface or interior of an object facing its user for interaction; and a ``system side"---where other hardware such as electronics may be connected.  We refer to a pipe which is ``open on the user side'' to have its contents \emph{physically accessible} to a user \emph{at interaction time}.  ``Closed on the user side'' implies physically cut off from the user.  Similarly with the system side.  User or system manipulation of pipe contents are possible even without physical access, e.g., via soundwaves.

@@

\subsection{Design of Pipes}
Pipe design may emphasize exterior connection points and/or interior paths.  Our maze (see Figure \ref{fig:maze}) requires specific terminals (the start and end of the maze) as well as a specific path for its tubes (the maze itself).  Alternatively, the neon sign's output in Figure \ref{fig:neon} is based only on the \emph{path} of the pipe.  Focused on just the exterior features is the touch sensitive toy in Figure \ref{fig:toys}, where pipes must exit the toy at the frontal lobe and parietal lobes to make those \emph{specific locations} touch-sensitive.  A pipe for weight modification does require specific terminals or a specific path (see Figure \ref{fig:openings}D).
